Data Preparation

### 2019-01-10 Data Preparation.Rmd
debugging import d_transcript

```{r Data Import}

x <- read_csv("Raw Grades/grades1.csv", col_types = cols())
t1 <- read.csv("Raw Grades/grades1.csv",na.strings=c("","NA"))
t2 <- read.csv("Raw Grades/grades2.csv",na.strings=c("","NA"))
d_dirt <-rbind(t1, t2)
d_dirt <- d_dirt[!duplicated(d_dirt),] #could use distinct() from dplyr
```

>>>>

```{r import d_transcript}
d_transcript <-rbind(read_csv("Raw Grades/grades1.csv", col_types = cols()),
                     read_csv("Raw Grades/grades2.csv", col_types = cols())) %>%
  distinct()
```
